Supporting Information - Tackling inconsistencies among freshwater invertebrate trait databases: Harmonising across continents and aggregating taxonomic resolution

### 2022-03-26 Paper/Submission_new/Latex_Supplementary_File.tex
26.03: Updated paper files, most recent in Submission_new

\title{Supporting Information - Tackling discrepancies in freshwater invertebrate trait databases: Harmonising across continents and aggregating taxonomic resolution}
\author[1]{Stefan Kunz}
\author[2]{Ben J. Kefford}
\author[3]{Astrid Schmidt-Kloiber}
\author[4]{Christoph D. Matthaei}
\author[5]{Philippe Usseglio-Polatera}
\author[3]{Wolfram Graf}
\author[6]{N. LeRoy Poff}
\author[7]{Leon Metzeling}
\author[8]{Laura Twardochleb}
\author[9]{Charles P. Hawkins}
\author[1]{Ralf B. Schäfer}
\affil[1]{Institute for Environmental Sciences, University of Koblenz-Landau, Landau, Germany}
\affil[2]{Centre for Applied Water Science, Institute for Applied Ecology, University of Canberra, Canberra, Australia}
\affil[3]{Institute of Hydrobiology and Aquatic Ecosystem Management, University of Natural Resources and Life Sciences Vienna (BOKU), Vienna, Austria}
\affil[4]{Department of Zoology, University of Otago, Dunedin, New Zealand}
\affil[5]{University of Lorraine, CNRS, LIEC, Metz, France}
\affil[6]{Department of Biology, Colorado State University, Fort Collins, USA}
\affil[7]{Environment Protection Authority Victoria, Applied Sciences Division, Macleod, Australia}
\affil[8]{Department of Fisheries and Wildlife, Michigan State University, East Lansing, USA}
\affil[9]{Department of Watershed Sciences, National Aquatic Monitoring Center, and the Ecology Center, Utah State University, Logan, USA}
\date{}

@@

\subsection*{Effects of harmonisation and trait aggregation on inferences regarding trait-environment relationships}

\begin{table}[H]
    \centering
    \caption{Mean, median and standard deviation of the affinities of traits that were responsive to the salinity gradient in the original study but not in the re-analysis using the harmonised European trait dataset.} 
    \label{tab:SI_resp_traits_summary_stats}
    \begin{tabular}{l|l|c|c|c|c}
    \toprule[.1em]
    Type & Trait & Mean & Median & SD & Responsive? \\ 
    \toprule[.1em]
    Stepw\_median & Shredder & 0.20 & 0.14 & 0.25 & No \\ 
      Stepw\_mean & Shredder & 0.18 & 0.12 & 0.22 & No\\ 
      Direct\_median & Shredder & 0.21 & 0.14 & 0.25 & No\\ 
      Direct\_mean & Shredder & 0.19 & 0.14 & 0.22 & No\\ 
      Weighted & Shredder & 0.19 & 0.14 & 0.22 & No \\ 
      Harmonised; not\_aggregated & Shredder & 0.18 & 0.12 & 0.24 & No \\ 
      Original & Shredder & 0.25 & 0.14 & 0.32 & Yes\\ 
      \midrule
      Stepw\_median & Gills & 0.30 & 0.27 & 0.32 & Yes\\ 
      Stepw\_mean & Gills & 0.29 & 0.22 & 0.32 & Yes\\ 
      Direct\_median & Gills & 0.30 & 0.30 & 0.32 & Yes\\ 
      Direct\_mean & Gills & 0.30 & 0.30 & 0.32 & Yes\\ 
      Weighted & Gills & 0.30 & 0.30 & 0.32 & Yes\\ 
      Harmonised; not\_aggregated & Gills & 0.30 & 0.25 & 0.32 & No \\ 
      Original & Gills & 0.28 & 0.00 & 0.33 & Yes \\ 
      \midrule
      Stepw\_median & Short life cycle & 0.64 & 0.75 & 0.39 & No \\ 
      Stepw\_mean & Short life cycle & 0.64 & 0.79 & 0.39 & No \\ 
      Direct\_median & Short life cycle & 0.67 & 0.75 & 0.37 & Yes \\ 
      Direct\_mean & Short life cycle & 0.67 & 0.79 & 0.38 & Yes \\ 
      Weighted & Short life cycle & 0.67 & 0.79 & 0.38 & Yes\\ 
      Harmonised; not\_aggregated & Short life cycle & 0.64 & 0.75 & 0.40 & Yes \\ 
      Original & Short life cycle & 0.64 & 0.75 & 0.40 & Yes \\ 
      \midrule
      Stepw\_median & Long life cylce & 0.36 & 0.25 & 0.39 & No \\ 
      Stepw\_mean & Long life cylce & 0.36 & 0.21 & 0.39 & No \\
      Direct\_median & Long life cylce & 0.33 & 0.25 & 0.37 & Yes\\ 
      Direct\_mean & Long life cylce & 0.33 & 0.21 & 0.38 & Yes \\ 
      Weighted & Long life cylce & 0.33 & 0.21 & 0.38 & Yes \\ 
      Harmonised; not\_aggregated & Long life cylce & 0.36 & 0.25 & 0.40 & Yes \\ 
      Original & Long life cylce & 0.36 & 0.25 & 0.40 & Yes\\ 
    \bottomrule
    \end{tabular}
\end{table}

\begin{figure}[H]
    \centering
    \includegraphics[width=18.5cm, height=16cm]{boxplot_scores_combined_REMAIN_SI.png}
    \caption{RDA of traits constrained by electric conductivity for the data aggregated with \textit{direct\_agg \textsubscript{mean}}, \textit{stepwise\_agg \textsubscript{mean}}, and \textit{weighted\_agg}. Shown are boxplots of the site scores along the conductivity axis. The rug on the right side of each plot indicates species scores of the traits on the conductivity axis. For more details see Figure 6. %\ref{fig:boxplot_scores_on_constrained_axis}. 
    Abbreviations: lcd, life cycle duration; nr.cy, potential number of cycles per year.}
    \label{fig:boxplots_scores_on_constrained_axis_REMAIN}
\end{figure}

@@

We selected the ecologically relevant traits identified by \citet{szocs_effects_2014} that increased (shredder, life cycle duration $ > 1 $ year, gills, bi/multivoltine, ovoviviparity) or decreased (univoltine, eggs in clutches/cemented or fixed, life cycle duration $ <= 1$ year) with increasing salinity and used these in the fourth corner analysis. The selected traits have also reacted to salinity in other studies (but see the discussion in \citet{szocs_effects_2014}). 
For some sites, environmental and abundance data have been sampled multiple times per year. \citet{szocs_effects_2014} used the full data and did not consider repeated sampling. We applied two analysis: one where we did not consider multiple samplings. And second where we selected, for the sites with multiple samplings, only those sampling events with the highest macroinvertebrate abundances per year and accordingly only used the conductivity data for these sampling events (this was not done for the RDA approach).Fourth corner analysis was carried out in R with the \textit{fourthcorner()} function from the ade4 package.
With the fourth corner analysis fewer trait-conductivity relationships than with the RDA approach were detected. With the original dataset significant relationships to conductivity were found for the traits shredder and ovoviviparity. In three out of the six aggregated and harmonised datasets (\textit{direct\_agg\textsubscript{mean}}, \textit{weighted\_agg}, harmonised (not aggregated)) four to five significant relationships (for the traits shredder, univoltinism, bi/multivoltine, ovoviviparity, and aquatic oviposition) were detected. In the remaining three datasets (\textit{stepwise\_agg\textsubscript{median}}, \textit{stepwise\_agg\textsubscript{mean}}, and \textit{direct\_agg\textsubscript{median}}) two significant relationships for the traits univoltinism and bi/multivoltinism were detected. Results were only slightly different when not considering multiple samplings (original dataset: one significant trait-conductivity relationship, others three to four). For the significant trait-conductivity relationships, the classification into characteristic traits for downstream and upstream sites was consistent with the results of the RDA analysis.

>>>>

\title{Supporting Information - Tackling inconsistencies among freshwater invertebrate trait databases: Harmonising across continents and aggregating taxonomic resolution}
\author[1]{Stefan Kunz}
\author[2]{Ben J. Kefford}
\author[3]{Astrid Schmidt-Kloiber}
\author[4]{Christoph D. Matthaei}
\author[5]{Philippe Usseglio-Polatera}
\author[3]{Wolfram Graf}
\author[6]{N. LeRoy Poff}
\author[7]{Leon Metzeling}
\author[8]{Laura Twardochleb}
\author[9]{Charles P. Hawkins}
\author[1]{Ralf B. Schäfer}
\affil[1]{Institute for Environmental Sciences, University of Koblenz-Landau, Landau, Germany}
\affil[2]{Centre for Applied Water Science, Institute for Applied Ecology, University of Canberra, Canberra, Australia}
\affil[3]{Institute of Hydrobiology and Aquatic Ecosystem Management, University of Natural Resources and Life Sciences Vienna (BOKU), Vienna, Austria}
\affil[4]{Department of Zoology, University of Otago, Dunedin, New Zealand}
\affil[5]{University of Lorraine, CNRS, LIEC, Metz, France}
\affil[6]{Department of Biology, Colorado State University, Fort Collins, USA}
\affil[7]{Environment Protection Authority Victoria, Applied Sciences Division, Macleod, Australia}
\affil[8]{Department of Fisheries and Wildlife, Michigan State University, East Lansing, USA}
\affil[9]{Department of Watershed Sciences, National Aquatic Monitoring Center, and the Ecology Center, Utah State University, Logan, USA}
\date{}

@@

\subsection*{Effects of harmonisation and trait aggregation on inferences regarding trait-environment relationships}
\label{sec:effects_harmonisation_trait_env_rel}

\begin{figure}[H]
    \centering
    \includegraphics[width=18.5cm, height=15cm]{boxplot_scores_combined_REMAIN_SI.png}
    \caption{RDA of traits constrained by electric conductivity for the data aggregated with \textit{direct\_agg \textsubscript{mean}}, \textit{stepwise\_agg \textsubscript{mean}}, and \textit{weighted\_agg}. Shown are boxplots of the site scores along the conductivity axis. The rug on the right side of each plot indicates species scores of the traits on the conductivity axis. For more details see Figure 6. %\ref{fig:boxplot_scores_on_constrained_axis}. 
    Abbreviations: lcd, life cycle duration; nr.cy, potential number of cycles per year.}
    \label{fig:boxplots_scores_on_constrained_axis_REMAIN}
\end{figure}

@@

We selected the ecologically relevant traits identified by \citet{szocs_effects_2014} that increased (shredder, life cycle duration $ > 1 $ year, gills, bi/multivoltine, ovoviviparity) or decreased (univoltine, eggs in clutches/cemented or fixed, life cycle duration $ <= 1$ year) with increasing salinity and used these in the fourth corner analysis. The selected traits also responded to salinity in other studies (but see \cite{szocs_effects_2014}).

Environmental and abundance data have been sampled multiple times per year in 12 of 15 sites. \citet{szocs_effects_2014} used the full data and ignored repeated sampling. To avoid temporal pseudoreplication, we selected, for all sites with multiple samplings only the sampling event with the highest macroinvertebrate abundance of each year and the corresponding conductivity data. Fourth corner analysis was carried out in R with the \textit{fourthcorner()} function from the ade4 package.

As expected, the fourth corner analysis detected fewer trait-conductivity relationships than the RDA approach. With the original dataset, a significant relationship to conductivity were found for the trait ovoviviparity (0.042) and almost for the trait shredder a p-value close to the significance level (0.077). In four out of the six aggregated and harmonised datasets (\textit{direct\_agg\textsubscript{mean}}, \textit{stepwise\_agg\textsubscript{mean}}, \textit{stepwise\_agg\textsubscript{median}}, harmonised (not aggregated)) four significant relationships (for the traits univoltinism, bi/multivoltine, ovoviviparity, and aquatic oviposition) were detected. In the remaining two datasets (\textit{direct\_agg\textsubscript{median}}, \textit{weighted\_agg}), two significant relationships for the traits univoltinism and bi/multivoltinism were detected (Table \ref{stab:fc_selected_reduced}). The results were only slightly different when multiple samplings were ignored (original dataset: four significant trait-conductivity relationship (shredders, univoltine, bi-multivoltine, ovoviviparity), other datasets two to four, Table \ref{stab:fc_selected_full}). For all significant trait-conductivity relationships, the classification into characteristic traits for downstream and upstream sites was consistent with the results of the RDA analysis.

\begin{longtable}[H]{m{2.6cm}|m{7.3cm}|m{1cm}|m{1.4cm}|m{1.5cm}|m{1.5cm}}
    \caption{Results of the fourth corner analysis, after accounting for multiple samplings per year, with the original dataset, harmonised (not aggregated), and aggregated trait datasets.}
    \label{stab:fc_selected_reduced}
    Dataset & Test & Obs & Std.Obs & Pvalue & Pvalue.adj \\ 
      stepw\_median & cond / feed\_shredder & 0.39 & 1.75 & 0.08 & 0.246 \\ 
      stepw\_median & cond / resp\_gil & 0.47 & 1.81 & 0.06 & 0.224 \\ 
      stepw\_median & cond / volt\_uni & -0.56 & -2.15 & 0.01 & 0.05 * \\ 
      stepw\_median & cond / volt\_bi\_multi & 0.56 & 2.19 & 0.01 & 0.048 * \\ 
      stepw\_median & cond / ovip\_aqu & -0.53 & -2.16 & 0.01 & 0.045 * \\ 
      stepw\_median & cond / ovip\_ovo & 0.54 & 2.17 & 0.01 & 0.045 * \\ 
      stepw\_median & cond / Life cycle duration $<=$ 1 year & -0.32 & -1.23 & 0.26 & 0.518 \\ 
      stepw\_median & cond / Life cycle duration $>$ 1 year & 0.32 & 1.23 & 0.26 & 0.518 \\
      stepw\_mean & cond / feed\_shredder & 0.39 & 1.80 & 0.06 & 0.2 \\ 
      stepw\_mean & cond / resp\_gil & 0.47 & 1.84 & 0.05 & 0.2 \\ 
      stepw\_mean & cond / volt\_uni & -0.56 & -2.26 & 0.01 & 0.042 * \\ 
      stepw\_mean & cond / volt\_bi\_multi & 0.57 & 2.26 & 0.01 & 0.042 * \\ 
      stepw\_mean & cond / ovip\_aqu & -0.53 & -2.21 & 0.01 & 0.05 * \\ 
      stepw\_mean & cond / ovip\_ovo & 0.54 & 2.22 & 0.01 & 0.05 * \\ 
      stepw\_mean & cond / Life cycle duration $<=$ 1 year & -0.33 & -1.31 & 0.21 & 0.426 \\ 
      stepw\_mean & cond / Life cycle duration $>$ 1 year & 0.33 & 1.31 & 0.21 & 0.426 \\ 
      direct\_median & cond / feed\_shredder & 0.38 & 1.73 & 0.09 & 0.27 \\ 
      direct\_median & cond / resp\_gil & 0.47 & 1.82 & 0.05 & 0.216 \\ 
      direct\_median & cond / volt\_uni & -0.56 & -2.25 & 0.01 & 0.035 * \\ 
      direct\_median & cond / volt\_bi\_multi & 0.57 & 2.28 & 0.00 & 0.032 * \\ 
      direct\_median & cond / ovip\_aqu & -0.53 & -2.27 & 0.02 & 0.055 . \\ 
      direct\_median & cond / ovip\_ovo & 0.54 & 2.28 & 0.01 & 0.055 . \\ 
      direct\_median & cond / Life cycle duration $<=$ 1 year & -0.34 & -1.38 & 0.20 & 0.39 \\ 
      direct\_median & cond / Life cycle duration $>$ 1 year & 0.34 & 1.38 & 0.20 & 0.39 \\ 
      direct\_mean & cond / feed\_shredder & 0.38 & 1.78 & 0.07 & 0.225 \\ 
      direct\_mean & cond / resp\_gil & 0.47 & 1.92 & 0.04 & 0.152 \\ 
      direct\_mean & cond / volt\_uni & -0.56 & -2.22 & 0.01 & 0.04 * \\ 
      direct\_mean & cond / volt\_bi\_multi & 0.57 & 2.26 & 0.01 & 0.04 * \\ 
      direct\_mean & cond / ovip\_aqu & -0.53 & -2.33 & 0.01 & 0.045 * \\ 
      direct\_mean & cond / ovip\_ovo & 0.54 & 2.20 & 0.01 & 0.042 * \\ 
      direct\_mean & cond / Life cycle duration $<=$ 1 year & -0.34 & -1.42 & 0.17 & 0.342 \\ 
      direct\_mean & cond / Life cycle duration $>$ 1 year & 0.34 & 1.42 & 0.17 & 0.342 \\
      weighted & cond / feed\_shredder & 0.38 & 1.69 & 0.09 & 0.261 \\ 
      weighted & cond / resp\_gil & 0.47 & 1.90 & 0.04 & 0.156 \\ 
      weighted & cond / volt\_uni & -0.56 & -2.23 & 0.01 & 0.03 * \\ 
      weighted & cond / volt\_bi\_multi & 0.57 & 2.46 & 0.00 & 0.024 * \\ 
      weighted & cond / ovip\_aqu & -0.53 & -2.19 & 0.01 & 0.055 . \\ 
      weighted & cond / ovip\_ovo & 0.54 & 2.20 & 0.01 & 0.055 . \\ 
      weighted & cond / Life cycle duration $<=$ 1 year & -0.34 & -1.34 & 0.21 & 0.414 \\ 
      weighted & cond / Life cycle duration $>$ 1 year & 0.34 & 1.34 & 0.21 & 0.414 \\
      not\_aggregated & cond / feed\_shredder & 0.41 & 1.83 & 0.05 & 0.188 \\ 
      not\_aggregated & cond / resp\_gil & 0.47 & 1.88 & 0.05 & 0.188 \\ 
      not\_aggregated & cond / volt\_uni & -0.57 & -2.16 & 0.01 & 0.035 * \\ 
      not\_aggregated & cond / volt\_bi\_multi & 0.58 & 2.21 & 0.00 & 0.024 * \\ 
      not\_aggregated & cond / ovip\_aqu & -0.55 & -2.24 & 0.01 & 0.045 * \\ 
      not\_aggregated & cond / ovip\_ovo & 0.55 & 2.25 & 0.01 & 0.045 * \\ 
      not\_aggregated & cond / Life cycle duration $<=$ 1 year & -0.33 & -1.25 & 0.22 & 0.446 \\ 
      not\_aggregated & cond / Life cycle duration $>$ 1 year & 0.33 & 1.25 & 0.22 & 0.446 \\
      original & cond / Feeding habits shredder & 0.54 & 2.19 & 0.01 & 0.077 . \\
      original & cond / Respiration gill & 0.47 & 1.83 & 0.05 & 0.255 \\ 
      original & cond / Potential number of cycles per year 1 & -0.48 & -1.83 & 0.05 & 0.255 \\ 
      original & cond / Potential number of cycles per year $>$ 1 & 0.49 & 1.91 & 0.04 & 0.222 \\
      original & cond / Reproduction ovoviviparity & 0.58 & 2.39 & 0.01 & 0.042 * \\ 
      original & cond / Reproduction clutches, cemented or fixed & -0.33 & -1.27 & 0.23 & 0.612 \\
      original & cond / Life cycle duration $<=$ 1 year & -0.33 & -1.31 & 0.20 & 0.612 \\ 
      original & cond / Life cycle duration $>$ 1 year & 0.33 & 1.31 & 0.20 & 0.612 \\          

\begin{longtable}[H]{m{2.6cm}|m{7.3cm}|m{1cm}|m{1.4cm}|m{1.5cm}|m{1.5cm}}
    \caption{Results of the fourth corner analysis without accounting for multiple samplings per year, with the original dataset, harmonised, and aggregated trait datasets.}
    \label{stab:fc_selected_full}
    Dataset & Test & Obs & Std.Obs & Pvalue & Pvalue.adj \\ 
      stepw\_median & cond / feed\_shredder & 0.33 & 1.68 & 0.08 & 0.24 \\ 
      stepw\_median & cond / resp\_gil & 0.39 & 1.79 & 0.06 & 0.24 \\ 
      stepw\_median & cond / volt\_uni & -0.52 & -2.41 & 0.00 & 0.028 * \\ 
      stepw\_median & cond / volt\_bi\_multi & 0.53 & 2.50 & 0.00 & 0.024 * \\ 
      stepw\_median & cond / ovip\_aqu & -0.46 & -2.44 & 0.01 & 0.065 . \\ 
      stepw\_median & cond / ovip\_ovo & 0.46 & 2.75 & 0.01 & 0.06 . \\ 
      stepw\_median & cond / Life cycle duration $<=$ 1 year & -0.28 & -1.26 & 0.22 & 0.446 \\ 
      stepw\_median & cond / Life cycle duration $>$ 1 year & 0.28 & 1.26 & 0.22 & 0.446 \\ 
      stepw\_mean & cond / feed\_shredder & 0.33 & 1.81 & 0.05 & 0.216 \\ 
      stepw\_mean & cond / resp\_gil & 0.39 & 1.74 & 0.07 & 0.216 \\ 
      stepw\_mean & cond / volt\_uni & -0.53 & -2.46 & 0.00 & 0.021 * \\ 
      stepw\_mean & cond / volt\_bi\_multi & 0.53 & 2.56 & 0.00 & 0.016 * \\ 
      stepw\_mean & cond / ovip\_aqu & -0.46 & -2.35 & 0.01 & 0.045 * \\ 
      stepw\_mean & cond / ovip\_ovo & 0.46 & 2.58 & 0.01 & 0.042 * \\ 
      stepw\_mean & cond / Life cycle duration $<=$ 1 year & -0.28 & -1.34 & 0.21 & 0.412 \\ 
      stepw\_mean & cond / Life cycle duration $>$ 1 year & 0.28 & 1.34 & 0.21 & 0.412 \\
      direct\_median & cond / feed\_shredder & 0.32 & 1.81 & 0.06 & 0.236 \\ 
      direct\_median & cond / resp\_gil & 0.39 & 1.81 & 0.06 & 0.236 \\ 
      direct\_median & cond / volt\_uni & -0.53 & -3.59 & 0.00 & 0.008 ** \\ 
      direct\_median & cond / volt\_bi\_multi & 0.54 & 3.65 & 0.00 & 0.008 ** \\ 
      direct\_median & cond / ovip\_aqu & -0.46 & -2.34 & 0.01 & 0.06 . \\ 
      direct\_median & cond / ovip\_ovo & 0.46 & 2.58 & 0.00 & 0.024 * \\ 
      direct\_median & cond / Life cycle duration $<=$ 1 year & -0.30 & -1.42 & 0.18 & 0.37 \\ 
      direct\_median & cond / Life cycle duration $>$ 1 year & 0.30 & 1.42 & 0.18 & 0.37 \\
      direct\_mean & cond / feed\_shredder & 0.32 & 1.67 & 0.09 & 0.27 \\ 
      direct\_mean & cond / resp\_gil & 0.39 & 1.82 & 0.06 & 0.228 \\ 
      direct\_mean & cond / volt\_uni & -0.53 & -3.54 & 0.00 & 0.008 ** \\ 
      direct\_mean & cond / volt\_bi\_multi & 0.54 & 2.62 & 0.00 & 0.014 * \\ 
      direct\_mean & cond / ovip\_aqu & -0.46 & -2.39 & 0.01 & 0.03 * \\ 
      direct\_mean & cond / ovip\_ovo & 0.46 & 2.67 & 0.00 & 0.014 * \\ 
      direct\_mean & cond / Life cycle duration $<=$ 1 year & -0.30 & -1.43 & 0.17 & 0.332 \\ 
      direct\_mean & cond / Life cycle duration $>$ 1 year & 0.30 & 1.43 & 0.17 & 0.332 \\
      weighted & cond / feed\_shredder & 0.32 & 1.69 & 0.09 & 0.268 \\ 
      weighted & cond / resp\_gil & 0.39 & 1.77 & 0.07 & 0.268 \\ 
      weighted & cond / volt\_uni & -0.53 & -3.57 & 0.00 & 0.008 ** \\ 
      weighted & cond / volt\_bi\_multi & 0.54 & 3.63 & 0.00 & 0.008 ** \\ 
      weighted & cond / ovip\_aqu & -0.46 & -2.37 & 0.00 & 0.012 * \\ 
      weighted & cond / ovip\_ovo & 0.46 & 2.61 & 0.00 & 0.015 * \\ 
      weighted & cond / Life cycle duration $<=$ 1 year & -0.30 & -1.40 & 0.20 & 0.398 \\ 
      weighted & cond / Life cycle duration $>$ 1 year & 0.30 & 1.40 & 0.20 & 0.398 \\
      not\_aggregated & cond / feed\_shredder & 0.35 & 1.82 & 0.06 & 0.236 \\ 
      not\_aggregated & cond / resp\_gil & 0.38 & 1.76 & 0.07 & 0.236 \\ 
      not\_aggregated & cond / volt\_uni & -0.53 & -3.80 & 0.00 & 0.008 ** \\ 
      not\_aggregated & cond / volt\_bi\_multi & 0.54 & 3.87 & 0.00 & 0.008 ** \\ 
      not\_aggregated & cond / ovip\_aqu & -0.47 & -2.37 & 0.01 & 0.03 * \\ 
      not\_aggregated & cond / ovip\_ovo & 0.48 & 2.72 & 0.00 & 0.024 * \\ 
      not\_aggregated & cond / Life cycle duration $<=$ 1 year & -0.29 & -1.40 & 0.19 & 0.372 \\ 
      not\_aggregated & cond / Life cycle duration $>$ 1 year & 0.29 & 1.40 & 0.19 & 0.372 \\
      original & cond / Feeding habits shredder & 0.45 & 2.17 & 0.01 & 0.042 * \\
      original & cond / Respiration gill & 0.38 & 1.80 & 0.06 & 0.252 \\  
      original & cond / Potential number of cycles per year 1 & -0.47 & -2.23 & 0.01 & 0.042 * \\ 
      original & cond / Potential number of cycles per year $>$ 1 & 0.47 & 2.26 & 0.01 & 0.042 * \\ 
      original & cond / Reproduction ovoviviparity & 0.51 & 2.89 & 0.00 & 0.016 * \\ 
      original & cond / Reproduction clutches, cemented or fixed & -0.34 & -1.58 & 0.13 & 0.402 \\  
      original & cond / Life cycle duration $<=$ 1 year & -0.29 & -1.41 & 0.18 & 0.402 \\ 
      original & cond / Life cycle duration $>$ 1 year & 0.29 & 1.41 & 0.18 & 0.402 \\
